The Impact of Educational Expenses of New Coders

### 2021-04-20 outputs/paper/paper.Rmd
Add model validation table

```{r}
#### RMSE with custom function ####
# Source: https://stackoverflow.com/questions/26237688/rmse-root-mean-square-deviation-calculation-in-r

RMSE <- function(error) {
  sqrt(mean(error^2)) 
}

RMSE(multiReg1$residuals)
RMSE(multiReg2$residuals)
RMSE(multiReg3$residuals)

# Model3 has the lowest RMSE among the 3 models => Model3 is the best!

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### RMSE with custom function ####

# Source: https://medium.com/dev-genius/metrics-for-evaluating-linear-regression-models-36df305510d9
# Source: https://stackoverflow.com/questions/26237688/rmse-root-mean-square-deviation-calculation-in-r

RSQ <- function(model) {
  return(summary(model)$r.squared)
}

MSE <- function(error) {
  return(mean(error^2))
}

RMSE <- function(error) {
  return(sqrt(mean(error^2))) 
}

vecModel <-
  c("Model (1)", "Model (2)", "Model (3)")

vecRSQ <- 
  c(RSQ(multiReg1), RSQ(multiReg2), RSQ(multiReg3))

vecMSE <-
  c(MSE(multiReg1$residuals), MSE(multiReg2$residuals), MSE(multiReg3$residuals))

vecRMSE <-
  c(RMSE(multiReg1$residuals), RMSE(multiReg2$residuals), RMSE(multiReg3$residuals))

dfModelValid <-
  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
  kable(caption = "Model validation",
        booktabs = TRUE,
        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 2:4, width = "3cm")

dfModelValid

# If R-squared is closer to 0 = Good!
# Model3 has the lowest RMSE among the 3 models => Model3 is the best!
